Supporting Information : Effect of copula on extinction risk

### 2019-02-27 MainText.Rmd
adding figures...continued

@@

>>>>

\listoffigures
\listoftables

@@

 <!--Generating maintext figures-->

 <!--FIG : age structure model results : linear, nonlinear-->
\begin{figure}[!h]
\textbf{ \hspace{5.4 cm} (A) \hspace{4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured model $(A)$ linear ($\Omega = \infty$) and $(B)$ nonlinear ($\Omega = 100$), fecundity of adults and survival of eggs have either extreme left or extreme right tail dependence, numsims=10000. \label{fig_extrisk_agestr}}
\end{center}
\end{figure}

### 2019-02-27 SuppMat.Rmd
adding figures...continued

# Age structure model :

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

![Extinction risk from one patch linear age structured model (omg=Infinity), fecundity of adults and survival of eggs have either extreme left or extreme right tail dep. copula structure, numsims=10000.\label{fig_extrisk_lagestr_extremetail}](./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf){ width=40%, height=40% }

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

![Extinction risk from one patch non-linear age structured model (omg=100), fecundity of adults and survival of eggs have either extreme left or extreme right tail dep. copula structure, numsims=10000.\label{fig_extrisk_nlagestr_extremetail}](./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf){ width=40%, height=40% }

#Ricker model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

#Hassell Model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell_scl_1}](./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

#Maynard Smith Model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary_scl_0.8}](./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

# Pennycuick model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_pennycuick_r_vary_scl_1}](./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

# Verhulst model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=0.6); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf){ width=40%, height=40% }

# Austin Brewer model :

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}](./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

@@

>>>>

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf[1:26,]
xR<-las_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf[1:26,]
xR<-nlas_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

@@

@@

@@

@@

@@

<!--Ricker model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

<!--Hassell model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell_scl_1}](./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

<!--Maynard smith model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary_scl_0.8}](./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

<!--Pennycuick model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_pennycuick_r_vary_scl_1}](./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

<!--Verhulst model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_pennycuick_r_vary_scl_1}](./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_pennycuick_r_vary_scl_1}](./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

<!--Austin brewer model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}](./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

@@

```{r create_maintext_fig3,echo=F,results="hide"}

getplot<-function(x,rlist){
lasta<-dim(x)[3]
Af<-as.data.frame(x[,,1][1:6,])
Al<-as.data.frame(x[,,lasta][1:6,])

plot(Af$d,Af$risk_left,xlim=range(Af$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Af$d,Af$risk_right,type="b",col="blue")

mtext(paste0("r = ", round(rlist[1],5)))

plot(Al$d,Al$risk_left,xlim=range(Al$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Al$d,Al$risk_right,type="b",col="blue")
mtext(paste0("r = ", round(rlist[lasta],5)))

}

pdf("./Results/allmodel_ext_risk_local_disp.pdf",height=12,width=9)

op<-par(mfrow=c(6,3),mar=c(5.2,4.2,1.2,1.5))

x<-res_ricker_local
rlist<-ricker_extrisk_d0$r

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.6,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.5, b = 100, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 1, b = 3, sd = 0.8)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.1, b = 0.1, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist)

par(op)
dev.off()
```
